The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-11-01 ms.Rmd
add zoon package text, update figure

The ZOON project takes a different approach, instead defining only the core architecture of workflows, and interfacing with an open repository of community-contributed software modules.
Users can create new modules for any modelling method and integrate it into another analysis.

Similarly to programming languages such as R and Python, facilitating wider development of software will enable the whole research community to develop the software that it requires, rather than rely on the developers of the software they use to do it for them.
Unlike software packages for programming languages however, the ZOON project enforces a modular structure that ensures interoperability between contributed software modules.
This also helps to lower the bar for creating modules (each module is simply an R function with a set of required inputs and outputs) and facilitates automated testing of modules ot ensure software quality .

This paper introduces version 0.4-22 of the `zoon` R package, which can be dowloaded from CRAN and which encodes the majority of this functionality. First, we describe the modular structure of zoon workflows and demonstrate how completed `zoon` workflows can be shared, evaluated and extended.
Then we illustrate these concepts, and the contribution we hope `zoon` will make to SDM research, by recreating and extending two recent SDM analyses using `zoon` workflows.

@@

<!— link to powerpoint doc: https://www.dropbox.com/s/afjpv8v6na9y56e/diagrams.pptx?dl=0-->

@@

The five module types, corresponding to the five key steps of an SDM anaysis are:

>>>>

The ZOON project takes a different approach, instead defining only the core architecture of workflows, and interfacing with an open repository of community-contributed software modules.
Users can create new modules for any modelling method and integrate it into another analysis. 
Similarly to programming languages such as R and Python, facilitating wider development of software will enable the whole research community to develop the software that it requires, rather than rely on the developers of the software they use to do it for them.
Unlike software packages for programming languages however, the ZOON project enforces a modular structure that ensures interoperability between contributed software modules.
This also helps to lower the bar for creating modules (each module is simply an R function with a set of required inputs and outputs) and facilitates automated testing of modules ot ensure software quality.

@@

<!— link to powerpoint doc: https://www.dropbox.com/s/p7rqww2v0h3a7np/diagrams.pptx?dl=0-->

@@

The five module types, corresponding to the five key steps of an SDM analysis are:
